\section{About Project}

\subsection{Title}
\textbf{Automated Cooking Assistant with AI}

\subsection{Domain}
Artificial Intelligence, Food Technology, Web Application Development, Personal Productivity, and Meal Planning.

\subsection{Aim}
\begin{itemize}
\item To develop an AI-based recipe generation system that suggests recipes from available ingredients and user preferences.
\item To provide an integrated cooking assistant with pantry management, saved recipes, meal planning, and shopping list support.
\end{itemize}

\subsection{Objective}
The objective of this project is to build a secure and user-friendly web application that generates personalized recipes, stores user preferences, manages pantry items, saves useful recipes, plans meals, and prepares shopping lists so that users can make better use of available ingredients and reduce daily meal planning effort.

\subsection{Problem Statement}
Many users find it difficult to decide what to cook with ingredients already available at home. The decision becomes harder when dietary restrictions, preferred cuisine, cooking time, and serving size must also be considered.

Existing recipe websites mainly depend on manual search and fixed recipe collections. They often do not combine pantry tracking, AI-based recipe creation, meal planning, saved recipes, and shopping lists in a single workflow.

This project proposes an intelligent web application that generates personalized recipes from available ingredients and user preferences. By integrating pantry management, meal planning, and shopping list support, the system improves convenience, reduces waste, and makes everyday cooking more organized.
