\begin{center}
\thispagestyle{plain}
\LARGE{\textbf{Acknowledgement}}\\[1cm]
\end{center}
\linespread{1.13}
\large{\paragraph{}
I would like to acknowledge all the teacher and friends who ever helped and assisted me throughout my project work.\newline \newline
First of all I would like to thank my respected guide \textbf {Prof. Dipali Bhusari}, introducing me throughout features needed. The time-to-time guidance, encouragement and valuable suggestion received from him are unforgettable in my life. This work would not have been possible without the enthusiastic response, insight and new idea from him.\newline \newline
Furthermore, I would like to thank respected \textbf{Dr. R. J. Patil}, Principal and  \textbf{Dr. A. A. Bhusari}, Head of Department of Master of Computer Applications for the guidance provided by them during my project work. I am also grateful to all the faculty members of Trinity Academy of Engineering, Pune for their support and cooperation. I would like to thank my lovely parent for time-to-time support and encouragement and valuable suggestion, and I would specify like to thank all my friends for their valuable suggestion and support. The acknowledgement world be incomplete without mention of the blessing of the almighty, which helped me in keeping high moral during difficult period.
}
\large{\paragraph{}
}
\begin{flushright}
    \begin{minipage}{0.45\textwidth}
        \textbf{Candidates:}\\[0.5cm]
        \textbf{Vaibhav  Shinde}\\
        \textbf{Shivam Gautam}\\
        \textbf{Rushab Yadav}\\
        \textbf{Suraj Yadav}\\[0.8cm]
        \textbf{Seat Numbers: \hrulefill}\\
        \textbf{Department of MCA}
    \end{minipage}
\end{flushright}
%\newpage
