\section{Conclusion and Future Work}

\subsection{Conclusion}

The AI Recipe Generator project provides a useful web-based solution for users who want to prepare recipes using available ingredients and personal preferences. The system supports user authentication, ingredient entry, recipe generation, pantry management, saved recipes, meal planning, and shopping list preparation. By using React.js for the frontend, Node.js and Express.js for the backend, PostgreSQL for database storage, and Google GenAI/Gemini API for AI-based recipe generation, the project offers a practical and user-friendly cooking assistant.

The system reduces the difficulty of deciding what to cook and helps users make better use of ingredients available at home. It also improves meal organization by allowing users to save recipes, plan meals, and manage shopping items. Overall, the project successfully meets its main objective of generating personalized recipes and supporting daily meal planning activities.

\subsection{Future Work}

In the future, the AI Recipe Generator can be improved with more advanced and intelligent features. Voice-based recipe search can be added so users can interact with the system hands-free while cooking. Image-based ingredient detection can also be implemented, allowing users to upload a photo of available ingredients and generate recipes automatically.

The system can be extended with calorie tracking, nutrition analysis, allergy alerts, recipe sharing, and multilingual support. Mobile application support can also be added for better accessibility. Further improvements may include offline recipe storage, advanced recommendation algorithms, and integration with grocery delivery platforms.
