\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=0.70in, bottom=0.70in, left=0.8in,right=0.80in]{geometry} 
\usepackage[pdftex]{graphicx} 
\usepackage[final]{pdfpages} 
\usepackage{float} 
\usepackage{hyperref}
\hypersetup{pdfborder = {0 0 0}}
%\usepackage{pslatex} 
\usepackage{array} 
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{ragged2e}
\usepackage{setspace}
%\usepackage{float}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{placeins}
\usepackage{microtype}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{pgfpages}
\usepackage[font=small,labelfont=bf]{caption}
\def\figurename{\textbf{Figure }}
%Includes "References" in the table of contents
\usepackage[nottoc]{tocbibind}
%for creating Abbreviation
\usepackage{acronym}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
 

%For the header and footer
\usepackage{fancyhdr}
%\fancypagestyle{fancy}{%
%\fancyfoot[L]{\emph{Department of Computer Engineering, SHORT NAME OF COLLEGE, Pune}} % except the center
%\fancyfoot[R]{\thepage}
%\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}
%}

\pagestyle{fancy}

\rhead{\large{Automated Cooking Assistant With AI}}
\fancyhead[L]{}
\fancyfoot[R]{\emph{Department of MCA}}
%\cfoot{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
%Page Border
% 
\addto\captionsenglish{\renewcommand*\contentsname{\centering{Contents}}}
\addto\captionsenglish{
\renewcommand{\listfigurename}{\textit{List of Figures}}
}

\addto\captionsenglish{
\renewcommand{\listtablename}{\textit{List of Tables}}
}



%GLOBAL SETTINGS OVER, DOCUMENT BEGINS
\begin{document}
\justifying
\onehalfspacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\setlist[itemize]{leftmargin=*, itemsep=3pt, topsep=3pt}
\setlist[enumerate]{leftmargin=*, itemsep=3pt, topsep=3pt}
\renewcommand{\arraystretch}{1.18}
%\renewcommand\bibname{References}
%\lhead{ }

%FROM HERE YOUR PAGES START GETTING ADDED
%\pgfpagesuselayout{boxed}
%\setlength{\parindent}{1cm}
% includes the cover page
%\pgfpagesuselayout{boxed}
%\input{project/cover.tex}
\pagenumbering{roman} %numbering before main content starts

\input{title.tex}
\newpage

% includes the certificate page
\input{certificate.tex} 
\addcontentsline{toc}{section}{\textit{Certificate}}
\newpage

% includes the acknowledgements page
\input{acknowledgements.tex}
\addcontentsline{toc}{section}{\textit{Acknowledgements}}
\newpage
\input{Declaration.tex}
\addcontentsline{toc}{section}{\textit{Declaration}}
\newpage

\input{abstract.tex} % adds the Research Methodology page
\addcontentsline{toc}{section}{\textit{Abstract}}
\newpage
%\stepcounter{page}


%TABLE OF CONTENTS AND LIST OF FIGURES ARE AUTOMATICALLY ADDED BY FOLLOWING COMMANDS
%ADD FIGURE OF TABLES IF YOU NEED TO, CHECK DOCUMENTATION

%To reset the Header & Footer for TOC and LOF
\pagestyle{empty}
%\addtocontents{toc}{\protect\thispagestyle{empty}}

\tableofcontents % adds Index Page 
\newpage
\listoffigures % adds List of Figures
\newpage
\listoftables  % adds List of Tables
%\addtocontents{lof}{}
\newpage
\input{Abbreviation.tex}
\addcontentsline{toc}{section}{\textit{List of Abbreviation}}
\newpage
\cleardoublepage

%And reset back the settings we choose for Header and Footer
\pagestyle{fancy}

\newpage
\pagenumbering{arabic} %reset numbering to normal for the main content

\input{About_Project.tex} % adds the introduction page
\newpage
\input{Introduction.tex}
\newpage

\input{literature-survey.tex} % adds the Literature Survey page

\newpage
%\input{project/req-analysis.tex}
%\input{project/system-design.tex}
\newpage
\input{SRS.tex}
\newpage
\input{Project_Plan.tex}
\newpage
\input{System_Design.tex}
\newpage
\input{advantageandapplication.tex}
%\input{project/implementation.tex} % adds the Project Design
%\input{project/screenshots.tex}
\newpage
\input{Software_Testing.tex}
\newpage
\input{Result.tex}
\newpage
\input{conclusion.tex} % adds the Scheduling and Planning page
\newpage

%\input{ref.tex} % adds the References page
\bibliographystyle{IEEEtran}
\begin{thebibliography}{9}

\bibitem{allrecipes}
Allrecipes, ``Recipes, Dinner Ideas and Menus.'' [Online]. Available: \url{https://www.allrecipes.com/}. Accessed: May 11, 2026.

\bibitem{mealime}
Mealime, ``Meal Planning App.'' [Online]. Available: \url{https://www.mealime.com/}. Accessed: May 11, 2026.

\bibitem{react}
Meta Open Source, ``React Documentation.'' [Online]. Available: \url{https://react.dev/}. Accessed: May 11, 2026.

\bibitem{vite}
Vite, ``Vite Documentation.'' [Online]. Available: \url{https://vite.dev/}. Accessed: May 11, 2026.

\bibitem{nodejs}
OpenJS Foundation, ``Node.js Documentation.'' [Online]. Available: \url{https://nodejs.org/en/docs}. Accessed: May 11, 2026.

\bibitem{express}
Express, ``Express.js Documentation.'' [Online]. Available: \url{https://expressjs.com/}. Accessed: May 11, 2026.

\bibitem{postgresql}
PostgreSQL Global Development Group, ``PostgreSQL Documentation.'' [Online]. Available: \url{https://www.postgresql.org/docs/}. Accessed: May 11, 2026.

\bibitem{sequelize}
Sequelize, ``Sequelize Documentation.'' [Online]. Available: \url{https://sequelize.org/docs/v6/}. Accessed: May 11, 2026.

\bibitem{jwt}
Auth0, ``JSON Web Tokens Introduction.'' [Online]. Available: \url{https://jwt.io/introduction}. Accessed: May 11, 2026.

\bibitem{googleai}
Google AI for Developers, ``Gemini API Documentation.'' [Online]. Available: \url{https://ai.google.dev/}. Accessed: May 11, 2026.

\bibitem{tailwind}
Tailwind Labs, ``Tailwind CSS Documentation.'' [Online]. Available: \url{https://tailwindcss.com/docs}. Accessed: May 11, 2026.

\end{thebibliography}


\newpage
\input{Internship.tex}
\addcontentsline{toc}{section}{Internship Report}
\newpage
\input{Publications.tex}
\addcontentsline{toc}{section}{Publication}
\newpage
\input{Plagiarism Report.tex}
\addcontentsline{toc}{section}{Plagiarism Report}
\end{document}
